Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
remove a space from the URL
remove a todo and make the url of the Lua mailing list post show up in the references

    \item[go:] A Monte-Carlo Go
        AI.\footnote{\url{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}
    \item[pyflate\_fast:] A BZ2 decoder.
    \item[raytrace\_simple:] A ray tracer.
    \item[richards:] The Richards benchmark.
    \item[spambayes:] A Bayesian spam filter.\footnote{\url{http://spambayes.sourceforge.net/}}
    \item[simpy\_expand:] A computer algebra system.
    \item[telco:] A Python version of the Telco decimal
        benchmark,\footnote{\url{http://speleotrove.com/decimal/telco.html}}
        using a pure Python decimal floating point implementation.
    \item[twisted\_names:] A DNS server benchmark using the Twisted networking
        framework.\footnote{\url{http://twistedmatrix.com/}}
\end{description}

@@

Mike Pall, the author of LuaJIT describes in a post to the lua-users mailing
list different technologies and techniques used in the implementation of
LuaJIT~\cite{Pall:2009}.\todo{decide if LuaJIT is a footnote or a reference and
fix website citation} Pall explains that guards in LuaJIT use a datastucture
called snapshots, similar to RPython's resume data, to store the information about
how to rebuild the state from a side-exit using the information in the snapshot
and the machine execution state. Pall also acknowledges that snapshot for
guards are associated with a large memory footprint. The solution used in
LuaJIT is to store sparse snapshots, avoiding the creation of snapshots for
every guard to reduce memory pressure. Snapshots are only created for guards
after updates to the global state, after control flow points from the original
program and for guards that are likely to fail. As an outlook Pall mentions the
plans to switch to compressed snapshots to further reduce redundancy.

>>>>

    \item[go:] A Monte-Carlo Go
        AI.\footnote{\url{http://shed-skin.blogspot.com/2009/07/disco-elegant-python-go-player.html}}
    \item[pyflate\_fast:] A BZ2 decoder.
    \item[raytrace\_simple:] A ray tracer.
    \item[richards:] The Richards benchmark.
    \item[spambayes:] A Bayesian spam filter.\footnote{\url{http://spambayes.sourceforge.net/}}
    \item[simpy\_expand:] A computer algebra system.
    \item[telco:] A Python version of the Telco decimal
        benchmark,\footnote{\url{http://speleotrove.com/decimal/telco.html}}
        using a pure Python decimal floating point implementation.
    \item[twisted\_names:] A DNS server benchmark using the Twisted networking
        framework.\footnote{\url{http://twistedmatrix.com/}}
\end{description}

@@

Mike Pall, the author of LuaJIT describes in a post to the lua-users mailing
list different technologies and techniques used in the implementation of
LuaJIT~\cite{Pall:2009}. Pall explains that guards in LuaJIT use a datastucture
called snapshots, similar to RPython's resume data, to store the information about
how to rebuild the state from a side-exit using the information in the snapshot
and the machine execution state. Pall also acknowledges that snapshot for
guards are associated with a large memory footprint. The solution used in
LuaJIT is to store sparse snapshots, avoiding the creation of snapshots for
every guard to reduce memory pressure. Snapshots are only created for guards
after updates to the global state, after control flow points from the original
program and for guards that are likely to fail. As an outlook Pall mentions the
plans to switch to compressed snapshots to further reduce redundancy.
